---
title: "Results"
author: "Alessandra Pescina"
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
B=1000
seed=2024
```

Load data
```{r}
numeric_clusters<-readRDS("data_final/numeric_clusters.RData")
survey_data<-readRDS("data_final/survey_cluster.RData")
survey_data<-as.data.frame(lapply(survey_data, as.factor))

survey_data$campo.studi[survey_data$campo.studi == "others"] <- "Others"
survey_data$campo.studi <- droplevels(survey_data$campo.studi)
survey_data$campo.studi<-as.factor(survey_data$campo.studi)
```


Let's introduce 2 new independent subjects and apply our classification algorithm

```{r}
person1_cl <- data.frame(
  sesso = "Maschio",
  age = "Over23",
  libri = "0",
  estero = "Si",
  strumento = "Si",
  lavoro = "Part time",
  stato="Italia",
  campo.studi="STEM (Science, Technology, Engineering, Mathematics)",
  importanza.musica="molto",
  come.ascolti.musica="ricerco spesso musica nuova e la considero un’attività a sé",
  concerti=">3",
  abitanti.citta="Più di 500 000 abitanti"
)


person2_cl<-data.frame(
  sesso = "Femmina",
  age = "Under23",
  libri = "1+",
  estero = "No",
  strumento = "No",
  lavoro = "no",
  stato="Italia",
  campo.studi="STEM (Science, Technology, Engineering, Mathematics)",
  importanza.musica="abbastanza",
  come.ascolti.musica="ascolto musica volentieri ma non mi allontano dai miei gusti",
  concerti="<=1",
  abitanti.citta="Meno di 100.000 abitanti"
)

newdata<-rbind(person1_cl, person2_cl)
```


```{r}
library(randomForest)
library(caret)
set.seed(2024)
fit_RF<-randomForest(as.factor(cluster) ~ ., data = survey_data, mtry=4, ntree=5000, replace=T)
fit_RF
```


```{r}
total<-rbind(survey_data[,-13], newdata)
total<-as.data.frame(lapply(total, as.factor))
newdata<-total[c(70,71),]
pred<- predict(fit_RF, newdata = newdata)
pred
```

Print the clusters of songs to which they will be assigned
```{r}
songs2<-numeric_clusters[numeric_clusters$cluster=="2",]
songs1<-numeric_clusters[numeric_clusters$cluster=="1",]
```

Select relevant ranges of descriptors previously computed by conformal prediction

```{r}
list_intervals = readRDS("../../conformal_intervals_byGroups.RData")
ind1<-paste0( "sesso",": ","Maschio",", VAR: ","popularity") #person1
ind2<-paste0( "sesso",": ","Femmina",", VAR: ","popularity") #person2
male_pop<-list_intervals[[ind1]]
female_pop<-list_intervals[[ind2]]
ind3<-paste0( "age",": ","Over22.5",", VAR: ","acousticness") #person1
ind4<-paste0( "age",": ","Under22.5",", VAR: ","acousticness") #person2
acu_Over23<-list_intervals[[ind3]]
acu_Under23<-list_intervals[[ind4]] 
ind5<-paste0( "lavoro",": ","no",", VAR: ","acousticness") #person2
ind6<-paste0( "lavoro",": ","Part time",", VAR: ","acousticness") #person1
acu_Nowork<-list_intervals[[ind5]]
acu_Parttime<-list_intervals[[ind6]]
ind7<-paste0( "libri",": ","1+",", VAR: ","danceability") #person2
ind8<-paste0( "libri",": ","0",", VAR: ","danceability") #person1
danc_libri1<-list_intervals[[ind7]]
danc_libri0<-list_intervals[[ind8]]
ind9<-paste0( "age",": ","Over22.5",", VAR: ","energy") #person1
ind10<-paste0( "age",": ","Under22.5",", VAR: ","energy") #person2
energy_Over23<-list_intervals[[ind9]]
energy_Under23<-list_intervals[[ind10]]
ind11<-paste0( "estero",": ","Si",", VAR: ","energy") #person1
ind12<-paste0( "estero",": ","No",", VAR: ","energy") #person2
energy_abroadSI<-list_intervals[[ind11]]
energy_abroadNO<-list_intervals[[ind12]]
ind13<-paste0( "estero",": ","Si",", VAR: ","instrumentalness") #person1
ind14<-paste0( "estero",": ","No",", VAR: ","instrumentalness") #person2
inst_abroadSI<-list_intervals[[ind13]]
inst_abroadNO<-list_intervals[[ind14]]
ind15<-paste0( "estero",": ","Si",", VAR: ","liveness") #person1
ind16<-paste0( "estero",": ","No",", VAR: ","liveness") #person2
live_abroadSI<-list_intervals[[ind15]]
live_abroadNO<-list_intervals[[ind16]]
ind17<-paste0( "sesso",": ","Maschio",", VAR: ","liveness") #person1
ind18<-paste0( "sesso",": ","Femmina",", VAR: ","liveness") #person2
male_live<-list_intervals[[ind17]]
female_live<-list_intervals[[ind18]]
ind19<-paste0( "age",": ","Over22.5",", VAR: ","loudness") #person1
ind20<-paste0( "age",": ","Under22.5",", VAR: ","loudness") #person2
loud_Over23<-list_intervals[[ind19]]
loud_Under23<-list_intervals[[ind20]] 
ind21<-paste0( "estero",": ","Si",", VAR: ","loudness") #person1
ind22<-paste0( "estero",": ","No",", VAR: ","loudness") #person2
loud_abroadSI<-list_intervals[[ind21]]
loud_abroadNO<-list_intervals[[ind22]]
ind23<-paste0( "strumento",": ","Si",", VAR: ","loudness") #person1
ind24<-paste0( "strumento",": ","No",", VAR: ","loudness") #person2
loud_strumentoSI<-list_intervals[[ind23]]
loud_strumentoNO<-list_intervals[[ind24]]
ind25<-paste0( "lavoro",": ","no",", VAR: ","tempo") #person2
ind26<-paste0( "lavoro",": ","Part time",", VAR: ","tempo") #person1
tempo_Nowork<-list_intervals[[ind25]]
tempo_Parttime<-list_intervals[[ind26]]
```

Filtrate songs of cluster one that are coherent with the expected ranges

```{r}
selected_songs1 <- songs1[
  songs1$popularity>= male_pop[1] & songs1$popularity <= male_pop[2] &
  songs1$acousticness>= acu_Over23[1] & songs1$acousticness<=acu_Over23[2] &
  songs1$acousticness>= acu_Parttime[1] & songs1$acousticness<=acu_Parttime[2] &
  songs1$danceability>= danc_libri0[1] & songs1$danceability<=danc_libri0[2] &
  songs1$energy>= energy_abroadSI[1] & songs1$energy<=energy_abroadSI[2] &
  songs1$energy>= energy_Over23[1] & songs1$energy<=energy_Over23[2] &
  songs1$instrumentalness>= inst_abroadSI[1] & songs1$instrumentalness<=inst_abroadSI[2] &
  songs1$liveness>= live_abroadSI[1] & songs1$liveness<=live_abroadSI[2] &
  songs1$liveness>= male_live[1] & songs1$liveness<=male_live[2] &
  songs1$loudness>= loud_abroadSI[1] & songs1$loudness<=loud_abroadSI[2] &
  songs1$loudness>= loud_Over23[1] & songs1$loudness<=loud_Over23[2] &
  songs1$loudness>= loud_strumentoSI[1] & songs1$loudness<=loud_strumentoSI[2] &
  songs1$tempo>= tempo_Parttime[1] & songs1$tempo<=tempo_Parttime[2] ,
]
selected_songs1_cleaned <- selected_songs1[!duplicated(selected_songs1[ colnames(selected_songs1) ]), ]
songs1_cleaned <- songs1[!duplicated(songs1[ colnames(songs1) ]), ]
```


Filtrate songs of cluster two that are coherent with the expected ranges
```{r}
selected_songs2 <- songs2[
 songs2$popularity>= female_pop[1] &songs2$popularity <= female_pop[2] &
 songs2$acousticness>= acu_Under23[1] &songs2$acousticness<=acu_Under23[2] &
 songs2$acousticness>= acu_Nowork[1] &songs2$acousticness<=acu_Nowork[2] &
 songs2$danceability>= danc_libri1[1] &songs2$danceability<=danc_libri1[2] &
 songs2$energy>= energy_abroadNO[1] &songs2$energy<=energy_abroadNO[2] &
 songs2$energy>= energy_Under23[1] &songs2$energy<=energy_Under23[2] &  
 songs2$instrumentalness>= inst_abroadNO[1] &songs2$instrumentalness<=inst_abroadNO[2] &  
 songs2$liveness>= live_abroadNO[1] &songs2$liveness<=live_abroadNO[2] &  
 songs2$liveness>= female_live[1] &songs2$liveness<=female_live[2] &
 songs2$loudness>= loud_abroadNO[1] &songs2$liveness<=loud_abroadNO[2] &
 songs2$loudness>= loud_Under23[1] &songs2$liveness<=loud_Under23[2] & 
 songs2$loudness>= loud_strumentoNO[1] &songs2$liveness<=loud_strumentoNO[2] & 
 songs2$tempo>= tempo_Nowork[1] &songs2$tempo<=tempo_Nowork[2] ,
]
selected_songs2_cleaned <- selected_songs2[!duplicated(selected_songs2[ colnames(selected_songs2) ]), ]
```

Check that the set of songs obtained for person 
```{r}
dim(songs1_cleaned)[1]/dim(songs1)[1]*100
dim(songs2_cleaned)[1]/dim(songs2)[1]*100

```

