---
title: "R Notebook"
output: html_notebook
---

# Import libraries
```{r}
# install.packages('pacman')
library(pacman)
pacman::p_load('spotifyr',  # To access the API
               'tidyverse', # Data wrangling and plots
               'plotly',    # Interactive plots
               'ggimage',   # Adding album covers to ggplot
               'kableExtra',# Format tables
               'httpuv',    # To be able to access the Spotify URL
               'httr')      # In case you want to access the API w/o
                            # the package

library(spotifyr)
library(dplyr )
```

# Get access
```{r}
CLIENT_ID='e862d6e00b244fe090bcb7bd0edd2fc8'
CLIENT_SECRET='d00ce12e600741ad8b614769eb52b7b8'

Sys.setenv(SPOTIFY_CLIENT_ID = CLIENT_ID)
Sys.setenv(SPOTIFY_CLIENT_SECRET = CLIENT_SECRET)

access_token <- get_spotify_access_token(
  client_id = Sys.getenv("SPOTIFY_CLIENT_ID"),
  client_secret = Sys.getenv("SPOTIFY_CLIENT_SECRET")
)
```

# LOAD DATA
```{r}
questionare <- read.csv("../../data/Questionario Spotify (Risposte) - Risposte del modulo 1.csv")

questionare=questionare[3:dim(questionare)[1],]  #la prima riga è vuota e la seconda ha un link non valido
lista_stringhe=questionare[,2]
valori_non_http <- which(!grepl("^http", lista_stringhe))

questionare = questionare[-valori_non_http,]


link_playlists = questionare[,"Incolla.qua.il.link"]
```
# manual corrections
```{r}
link_playlists[5]="https://open.spotify.com/playlist/37i9dQZF1F0sijgNaJdgit?si=ySYezdR1SrWx3Edh2_Gwzg"
```



## debug
```{r}
#link_playlists
```

# Function to extract tracks features
```{r}
extract_tracks <- function(spot_link){
  tracks <- get_playlist_audio_features(playlist_uris = spot_link)
  features=c(
            "track.name" ,
            "track.album.name",
            "track.album.artists",
            "track.album.release_date",
            "track.duration_ms" ,
            "track.popularity",
            "acousticness", #
            "danceability", #
            "energy", #
            "instrumentalness", #
            "liveness", #
            "loudness", #
            "speechiness", #
            "tempo", #
            "key", ##
            "mode", ##
            "track.duration_ms" ,##
            "valence",##
            "time_signature", #
            "track.id"  # used to add the tracks to another playlists
            )
  data = tracks[features]
  
  for(i in 1:dim(data)[1]){
    if(i%%500==0){
      Sys.sleep(50)
    }
    data[i,"artists"] = data[i,"track.album.artists"][[1]][[1]][3][1,]
    genres = get_artist(data[i,"track.album.artists"][[1]][[1]][[2]][1])$genres
    if(length(genres)!=0){
        for(j in 1:length(genres)){
           data[i,paste0("genre_",j)] = genres[j]
        }
    }
  }
  data$track.album.artists = NULL

  # move the artists column at the beginning
  data=data %>% relocate(artists, .after = track.name)
  return(data)
}
```
# create dataframe list
Note codice
".*/(.+)$"
è un'espressione regolare che corrisponde a una stringa che inizia con qualsiasi carattere (.*) seguito da una barra (/), e cattura quindi uno o più caratteri (.+) fino alla fine della stringa ($). Questo effettivamente cattura l'ultima parte di una stringa che segue l'ultima barra.


```{r}
data_tracks = list()
id_non_validi <- list()
counter = 1

for (l in link_playlists) {
  tryCatch({
    # Use regular expression to extract the identifier
    id <- sub(".*/(.+)$", "\\1", l)
    data_tracks[[id]] <- extract_tracks(id)
  }, error = function(e) {
    # Se si verifica un errore, salva l'id non valido
    id_non_validi <- c(id_non_validi, id)
    cat("Errore nell'elaborazione dell'ID:", id, "\n")
  })
  
  if(counter%%3==0){  # every 3 playlists(500 songs) stops for 50 seconds
  Sys.sleep(50)
  }
  
  
  print(counter)
  counter=counter+1
}
```


# Save data 

data of tracks will be saved separetly on csv files named with the link of the spotify playlist (only first 15 chars)
```{r}
for (i in seq_along(data_tracks)) {
  name = substr(names(data_tracks)[i], start = 1, stop = 15)
  write.csv(data_tracks[[i]], paste0("../../data/tracks_info_2/",name , ".csv"), row.names = FALSE)
}
```

# IGNORE

```{r}
file_name = "data_tracks"
file_name = paste0(file_name,".csv")

write.csv(data_tracks, file =paste0("../../data/",file_name), row.names = FALSE)
```
```{r}
# Store the data in a dataframe
EVERYTHING = "3EbHbn5D6oNFLJ5FrQKcAj?si=6ab30cd7e6794754"
ALTERNATIVE="39VgCTxGok4VIgIycgyTRq?si=f0ee9b71e9f048b2"
SHORT = "6zSzzHtzQxXVf9kuQXO3eS?si=7917643ebd854a5c"
AMICA_ALE = "0fCgMTSTRKPWUKp11pYQ6F?si=165f512ebe7b4a59"
ETTORE22 = "05oN1p78ynHAs0ulg4HvuF?si=069dd1d8a82b4d1e"




tracks <- get_playlist_audio_features(playlist_uris = ETTORE22)
head(tracks[,36])
dim(tracks)[1]
```



