---
title: 'Analysis by ecdf'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

## Loading numeric and survey data
```{r}
survey_data<-readRDS("../../data/Surveycleaned.RData")
numeric_data<-readRDS("../../data/data_numeric_cleaned2.RData")
```

```{r}
survey_data <- survey_data[order(survey_data$id), ]
numeric_data <-numeric_data[order(numeric_data$id), ]
```


## Merging dataset
```{r}
combined_data <- merge(numeric_data, survey_data, by.x = "id", by.y = "id")
```

standardize values *duration* and *year* in order to have consistent analysis
```{r}
min_max_normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}
  
combined_data$duration<-  min_max_normalize(combined_data[,12])
combined_data$year<-  min_max_normalize(combined_data[,13])
```

## Ecdf list per person
```{r}
names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  lines(edf_list[[i]], lwd = 0.5, cex = 0.1)

}}
```


## Ecdf list per person by category

### Sesso
```{r}
 sapply(combined_data, class)
```

```{r}

names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$sesso

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex =0.1)
  }
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}


```

### Come ascolti musica

```{r}
names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$come.ascolti.musica

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```
### Educazione

```{r}
names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$educazione

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```

### Campo Studi
qua non so se ha senso confrontare STEM con altro ma sicuramente i dati sono più significativi
in quanto del resto delle categorie non abbiano molti dati

```{r}
test<-survey_data$campo.studi!="STEM (Science, Technology, Engineering, Mathematics)"         
survey_data$campo.studi<-ifelse(test,"Altro","STEM (Science, Technology, Engineering, Mathematics)" )

names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$campo.studi
categorical<- na.omit(categorical)

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```
### Stato
```{r}

test<-survey_data$stato!="Italia"
survey_data$stato<-ifelse(test,"Estero","Italia")

names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$stato

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```

### Generi

```{r}


names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$genere

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```

### Strumento

```{r}


names_cov<-colnames(combined_data)
for (i in names_cov[2:13]){
  
covariate <-i
categorical<- survey_data$strumento

edf_list <- lapply(unique(combined_data$id), function(person_id) {
  person_data <- combined_data[combined_data$id == person_id, ]
  ecdf(person_data[[covariate]])
})

num_groups <- length(unique(categorical))
color_palette <- rainbow(num_groups)

unique_groups = unique(categorical)

plot(NULL, xlim = c(0, 1), ylim = c(0, 1),
     main = paste("EDF for", covariate),
     xlab = "Data Values", ylab = "Probability")

for (i in seq_along(edf_list)) {
  group_value <- categorical[i]
  lines(edf_list[[i]], lwd = 0.5, col = color_palette[unique_groups == group_value], cex = 0.1)}
legend("topright", legend = unique_groups, fill = color_palette,cex = 0.6, x.intersp = 0.7, y.intersp = 0.7)
}
```