---
title: 'Survey data'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(848)
```

## Load Data


```{r}
Survey_data = readRDS("../../data/Questionario_eng.RData")
Quest_data = readRDS("../../data/Questionario.RData")
```

##Rename cols

```{r}
names_cols<-c("età", "sesso", "educazione", "campo.studi", "stato", "libri", "lavoro", "importanza.musica", "genere", "come.ascolti.musica","quando.ascolti.musica", "concerti", "strumento", "sport", "estero", "politica", "hobby", "regione", "abitanti.città", "id" )
names(Quest_data)<-names_cols
names(Survey_data)<-names_cols
```

## Merging dataframes
```{r}
Data<-rbind(Quest_data, Survey_data)
```

```{r}
dataset_list = readRDS("../../data/data_list.RData")
id_keep<-names(dataset_list)
```

we keep only the rows corresponding to people having a proper playlist

```{r}
filtered_data <- Data[Data$id %in% id_keep, ]
```

## Adjusting factors

Grammar corrections..

```{r}
temp<-filtered_data$importanza.musica
temp[7]="tanto"
filtered_data$importanza.musica<-temp
```

```{r}
temp<-filtered_data$strumento
temp[11]="piano"
temp[29]="chitarra"
filtered_data$strumento<-temp
```


```{r}
temp<-filtered_data$politica
temp[c(68)]="Sì molto"
filtered_data$politica<-temp
```

```{r}
temp<-filtered_data$abitanti.città
temp[c(69)]= "Tra 100.000 e 500.000 abitanti"
temp[c(64,65,66,67,68,70)]="Più di 500 000 abitanti" 
temp[1]="Tra 100.000 e 500.000 abitanti"
filtered_data$abitanti.città<-temp
```

```{r}
temp<-filtered_data$estero
temp[c(1,64,65,66,67,68,69,70)]= "Europa occidentale"
filtered_data$estero<-temp
```

People not living in Italy or no longer living in Italy ->"/"
```{r}
temp<-filtered_data$regione
Lombardia<-c(5,9,13,15,17,19,25,27,29,33,35,41,43,45,53,55,59,61,63,4,6,8,12,14,18,20,22,36,40,42,44,46,48,50,52,54,56,58,60,62)
na<-c(11,23,34,47,64:70)
Lazio<-c(7,57,28,38)
Toscana<-c(1,21,37,16,30,31,32,49)
temp[Lombardia]<-"Lombardia"
temp[na]="/"
temp[Lazio]="Lazio"
temp[Toscana]="Toscana"
filtered_data$regione<-temp
```


Collecting people playing more then  one instrument
```{r}
index<-c(2,28,57,70)
filtered_data$strumento[index]="2+"

```

Converting to factors

```{r}
filtered_data$sesso<-as.factor(filtered_data$sesso)
filtered_data$educazione<-as.factor(filtered_data$educazione)
filtered_data$campo.studi<-as.factor(filtered_data$campo.studi)
filtered_data$libri<-as.factor(filtered_data$libri)
filtered_data$lavoro<-as.factor(filtered_data$lavoro)
filtered_data$importanza.musica<-as.factor(filtered_data$importanza.musica)
filtered_data$come.ascolti.musica<-as.factor(filtered_data$come.ascolti.musica)
filtered_data$strumento<-as.factor(filtered_data$strumento)
filtered_data$politica<-as.factor(filtered_data$politica)
filtered_data$abitanti.città<-as.factor(filtered_data$abitanti.città)
filtered_data$estero<-as.factor(filtered_data$estero)
filtered_data$regione<-as.factor(filtered_data$regione)
filtered_data$sport<-as.factor(filtered_data$sport)
```

Here nothing special, I had to adjust capslocks in order to have unique levels 
```{r}
col.stato<-filtered_data$stato
Italia<- c(1,2,3,4,5,6,8,9,10,12,13,14,15,16,17,18,19,20,21,22,24,25,26,27,28,29,30,31,32,33,35,36,37,38,39,40,41,42,43,44,45,46,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,67)
Svizzera<-c(7,23)
Germania<-c(34,70)
Olanda<-c(47)
Spagna<-c(11,68,69)
Canada<-c(64,65,66)
col.stato[Canada]="Canada"
col.stato[Italia]="Italia"
col.stato[Spagna]="Spagna"
col.stato[Svizzera]="Svizzera"

col.stato<-as.factor(col.stato)
levels(col.stato)
```
```{r}
filtered_data$stato<-col.stato
```

removing the guy with only 3 songs in the playlist
the one with id: "4YjSpxvniwzXvBB"

```{r}
filtered_data<-filtered_data[-75,]
```

So far we have:
id 
numeric -> età, concerti 
factors -> anything else

TODO
cosa non so trattare al momento
- hobby
- generi (aspetto divisione tancre)
- quando ascolti musica
- sport


## Visualize data

```{r}
summary(filtered_data)
```
Save processed data so far

```{r}
reduced<-filtered_data[,-c(9,11,14,17)]
```

```{r}
factor_columns<-c(2,3,4,5,6,7,8,9,11,12,13,14,15)
cols<-names(reduced[,factor_columns])
reduced_factors<-reduced[,factor_columns]
```


```{r}
names<-colnames(reduced_factors)
do_barplot<-function(i){
ggplot(as.data.frame(reduced_factors)) + 
  geom_bar(mapping = aes(x =reduced_factors[[i]], fill = reduced_factors[[i]]))+
    ggtitle(names[i])}


```

regà non mi andava la funzione in un ciclo for
```{r}
do_barplot(1)
do_barplot(2)
do_barplot(3)
do_barplot(4)
do_barplot(5)
do_barplot(6)
do_barplot(7)
do_barplot(8)
do_barplot(9)
do_barplot(10)
do_barplot(11)
do_barplot(12)
do_barplot(13)
```

