---
title: 'Permutation'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

```{r}
library(dplyr)
set.seed(53)
```


## Loading numeric and survey data
```{r}
survey_data<-readRDS("../../data/Surveycleaned.RData")
numeric_data<-readRDS("../../data/data_numeric_cleaned2.RData")
```


```{r}
perm_t_test=function(x,y,iter=1e3){
  
  T0=abs(mean(x)-mean(y))  # define the test statistic
  T_stat=numeric(iter) # a vector to store the values of each iteration
  x_pooled=c(x,y) # pooled sample
  n=length(x_pooled)
  n1=length(x)
  
  for(perm in 1:iter){ # loop for conditional MC
    # permutation:
    permutation <- sample(1:n)
    x_perm <- x_pooled[permutation]
    x1_perm <- x_perm[1:n1]
    x2_perm <- x_perm[(n1+1):n]
    # test statistic:
    T_stat[perm] <- abs(mean(x1_perm) - mean(x2_perm))
    
  }
  
  # p-value
  p_val <- sum(T_stat>=T0)/iter
  return(p_val)
}
```

## Test by geometric sample DO NOT USE


```{r}

my_perm<-function(cat1,cat2){
cols<-colnames(numeric_data)
res<-{ }

for (j in 1:12){
  p_value<-{ } 

  for (i in 1:100){
     
    selected_data_cat1 <- numeric_data %>%
        filter(id %in% cat1)

     cov1 <- selected_data_cat1 %>%
        group_by(id) %>%
        sample_n(1, weight = dgeom(1:n(), prob = 0.3), replace = TRUE) %>%
        pull(!!cols[j])

     
      selected_data_cat2 <- numeric_data %>%
        filter(id %in% cat2)

    
      cov2 <- selected_data_cat2 %>%
        group_by(id) %>%
        sample_n(1, weight = dgeom(1:n(), prob = 0.3), replace = TRUE) %>%
        pull(!!cols[j])

    p_value[i]<-perm_t_test(cov1,cov2)

}

  res[j]<-sum(p_value)/100
}
return (res)
}

```


## Mega Permutation, this useful only if we prove independence, DO NOT USE

```{r}
my_perm_mega<-function(cat1,cat2){
cols<-colnames(numeric_data)
res<-{ }

for (j in 1:12){

     
    selected_data_cat1 <- numeric_data %>%
        filter(id %in% cat1)

     cov1 <- selected_data_cat1[,j]

     
      selected_data_cat2 <- numeric_data %>%
        filter(id %in% cat2)

    
      cov2 <- selected_data_cat2[,j]
      
      res[j]<-perm_t_test(cov1,cov2)

}
return (res)
}
```

## Media Permutation, OFFICIAL ONE

```{r}
my_perm_median<-function(cat1,cat2){
cols<-colnames(numeric_data)
res<-{ }

for (j in 1:12){
     
    selected_data_cat1 <- numeric_data %>%
        filter(id %in% cat1)

     cov1 <- selected_data_cat1 %>%
        group_by(id) %>%
        summarize(mean_col_j = median(!!sym(cols[j]))) %>%
        pull()

  

     
      selected_data_cat2 <- numeric_data %>%
        filter(id %in% cat2)

    
      cov2 <- selected_data_cat2 %>%
        group_by(id) %>%
        summarize(mean_col_j = median(!!sym(cols[j]))) %>%
        pull()

      
    res[j]<-perm_t_test(cov1,cov2)

}
return (res)
}
```

### Permutation Test each num_cov by sex


```{r}
cat1<-survey_data$id[survey_data$sesso=="Maschio"]
cat2<-survey_data$id[survey_data$sesso=="Femmina"]

```

 
```{r}
res_sex<-my_perm_median(cat1,cat2)
res_sex
```

### Permutation Test each num_cov by field of study

```{r}
test<-survey_data$campo.studi!="STEM (Science, Technology, Engineering, Mathematics)"         
survey_data$campo.studi<-ifelse(test,"Others","STEM (Science, Technology, Engineering, Mathematics)")
temp<-survey_data$id[!is.na(survey_data$campo.studi)]
selected_campostudi <- survey_data$campo.studi[!is.na(survey_data$campo.studi)]
cat1<-temp[selected_campostudi =="STEM (Science, Technology, Engineering, Mathematics)"]
cat2<-temp[selected_campostudi =="Others"]
```


```{r}
res_fieldofstudy<-my_perm_median(cat1,cat2) 
res_fieldofstudy
```

### Permutation Test each num_cov by instrument

```{r}
cat1<-survey_data$id[survey_data$strumento=="Si"]
cat2<-survey_data$id[survey_data$strumento=="No"]

```


```{r}
res_instrument<-my_perm_median(cat1,cat2) #pvalue year 0.029
res_instrument
```

### Permutation Test each num_cov by country (not balanced)

```{r}
test<-survey_data$stato!="Italia"         
survey_data$stato<-ifelse(test,"Others","Italia")
temp<-survey_data$id[!is.na(survey_data$stato)]
selected_stato <- survey_data$stato[!is.na(survey_data$stato)]
cat1<-temp[selected_stato =="Italia"]
cat2<-temp[selected_stato =="Others"]
```


```{r}
res_country<-my_perm_median(cat1,cat2)
res_country 
```

### Permutation Test each num_cov by number of books

```{r}
test<-survey_data$libri!="0"         
survey_data$libri<-ifelse(test,"1+","0")
temp<-survey_data$id[!is.na(survey_data$libri)]
selected_libri <- survey_data$libri[!is.na(survey_data$libri)]
cat1<-temp[selected_libri =="0"]
cat2<-temp[selected_libri =="1+"]
```


```{r}
res_books<-my_perm_median(cat1,cat2)
res_books
```

### Permutation Test each num_cov by abroad 

```{r}
test<-survey_data$estero!="No"         
survey_data$estero<-ifelse(test,"Si","No")
temp<-survey_data$id[!is.na(survey_data$estero)]
selected_estero <- survey_data$estero[!is.na(survey_data$estero)]
cat1<-temp[selected_estero =="No"]
cat2<-temp[selected_estero =="Si"]
```


```{r}
res_abroad<-my_perm_median(cat1,cat2)
res_abroad
```

### Permutation Test each num_cov by age

```{r}
colnames(survey_data)[1] ="age"
# Count values below 22.5 in the 'age' column
values_below_23 <- sum(survey_data$age < 23, na.rm = TRUE)
values_below_23

# Count missing data in the 'age' column
missing_data_age <- sum(is.na(survey_data$age))
missing_data_age

```

```{r}
test<-survey_data$age < 23        
survey_data$age<-ifelse(test,"Under23","Over23")
temp<-survey_data$id[!is.na(survey_data$age)]
selected_age <- survey_data$age[!is.na(survey_data$age)]
cat1<-temp[selected_age =="Under23"]
cat2<-temp[selected_age =="Over23"]
```


```{r}
res_age<-my_perm_median(cat1,cat2)
res_age
```


### Permutation Test each num_cov by region

```{r}
test<-survey_data$regione!="nord"         
survey_data$regione<-ifelse(test,"centro-sud","nord")
temp<-survey_data$id[!is.na(survey_data$regione)]
selected_regione <- survey_data$regione[!is.na(survey_data$regione)]
cat1<-temp[selected_regione =="nord"]
cat2<-temp[selected_regione =="centro-sud"]
```


```{r}
res_region<-my_perm_median(cat1,cat2)
res_region
```

Let's bind the results in a dataframe
```{r}
res_perm<-rbind(res_sex,res_fieldofstudy, res_age, res_books, res_abroad, res_country,
                res_instrument, res_region)
cnames<-colnames(numeric_data[,-13])
colnames(res_perm)<-cnames
```

Let's assess if the category are balanced as well

country and region might give problems..

```{r}
selected_indices <- c(2,4,1,6,13,5,12,15)
selected_data <- survey_data[, selected_indices]


for (i in seq_along(selected_indices)) {

  barplot(table(selected_data[, i]), col = "lightblue",
          main = colnames(selected_data)[i], xlab = "", ylab = "Frequency")
}

```


## One-way Anova

```{r}
#Non parametric one way anova function
one_way_anova <- function(x, cat, iter=1e3){
  T_stat <- numeric(iter) 
  n <- length(x)
  fit <- aov(x ~ cat)
  T0 <- summary(fit)[[1]][1,4]
 
  
  for(perm in 1:iter){
    # Permutation:
    permutation <- sample(1:n)
    x_perm <- x[permutation]
    fit_perm <- aov(x_perm ~ cat)
  
    # Test statistic:
    T_stat[perm] <- summary(fit_perm)[[1]][1,4]
  }
  p_val <- sum(T_stat>=T0)/iter
  return (p_val)
} 

```



```{r}
#One way anova on all 12 covariates with extraction

my_one_way <- function(cat){
  res <- vector("numeric", length = 12)
  for (j in 1:12) {
    #missing
    res[j] <- one_way_anova(unlist(median_data[,j]), cat)
  }
  return(res)
}

```


```{r}
median_data <- numeric_data %>%
        group_by(id) %>%
        summarise(across(everything(), median))
     
```

```{r}
id_col<-median_data$id
median_data<-median_data[,-1]
median_data$id<-id_col

```


### Anova Permutation test for Work 

```{r}
res_work<-my_one_way(survey_data$lavoro)
res_work
```


### Anova Permutation test for Importance of music


```{r}
res_importance.music<-my_one_way(survey_data$importanza.musica)
res_importance.music
```

### Anova Permutiation test for How do you listen to music


```{r}
res_how.listen<-my_one_way(survey_data$come.ascolti.musica)
res_how.listen
```

### Anova Permutation test for Number of concerts

```{r}
# Define the breakpoints for the categories
breakpoints <- c(-Inf, 1, 3, Inf)

# Create a new categorical column based on the numeric_column
survey_data$concerti <- cut(survey_data$concerti, breaks = breakpoints, labels = c("<=1", "(1,3]", ">3"), include.lowest = TRUE)
```

rejecting H0: none. Possible to change the division of the data
```{r}
res_concerts<-my_one_way(survey_data$concerti)
res_concerts
```

### Anova Permutation for Number of inhabitants

```{r}
table(survey_data$abitanti.citta)

# Transform the column based on conditions
survey_data <- survey_data %>%
  mutate(
    abitanti.citta = case_when(
      abitanti.citta %in% c("Meno di 1000 abitanti", "Tra 1.000 e 10.000 abitanti", "Tra 10.000 e 100.000") ~ "Meno di 100.000 abitanti",
      TRUE ~ abitanti.citta
    )
  )
table(survey_data$abitanti.citta)
```
```{r}

survey_data <- survey_data %>%
  mutate(abitanti.citta= case_when(
    abitanti.citta %in% c("Meno di 1000 abitanti", "Tra 1.000 e 10.000 abitanti") ~ "Meno di 100.000 abitanti",
    abitanti.citta == "Tra 100.000 e 500.000 abitanti" ~ "Tra 100.000 e 500.000 abitanti",
    abitanti.citta == "Più di 500 000 abitanti" ~ "Più di 500 000 abitanti",
    TRUE ~ abitanti.citta  
  ))
table(survey_data$abitanti.citta)
```


```{r}
res_inhabitants<-my_one_way(survey_data$abitanti.citta)
res_inhabitants
```
### Anova Permutation for Genre

We consider only people in the most listened genres, since it doesn't make sense compare other genres with to few people (hiphop,pop,rock)

```{r}
genre_counts<-table(survey_data$genere)
selected_genres <- names(genre_counts[genre_counts > 10])

survey_data$genere[!(survey_data$genere %in% selected_genres)] <- NA

table(survey_data$genere)
```

```{r}
res_genre<-my_one_way(survey_data$genere)
res_genre
```

Let's bind results
```{r}
res_anova<-rbind(res_work,res_importance.music, res_how.listen, res_concerts, res_inhabitants, res_genre)
cnames<-colnames(numeric_data[,-13])
colnames(res_anova)<-cnames
```


```{r}
res<-rbind(res_perm,res_anova)
```

If we wanna use importanza.musica we need to rearrange somehow
```{r}
selected_indices <- c(7,8,10,11,16,9)
selected_data <- survey_data[, selected_indices]


for (i in seq_along(selected_indices)) {

  barplot(table(selected_data[, i]), col = "lightblue",
          main = colnames(selected_data)[i], xlab = "", ylab = "Frequency",cex.names = 0.7, las=2)
}

```


## Results 

Raga help non riesco a farlo stampare nell'ordine corretto,
volevo colorare di rosso i pvalue delle categorie significative con alpha=0.05

```{r}

threshold <- 0.05
condition0.05 <- ifelse(res< threshold, 1, 0)

condition0.05<-as.data.frame(condition0.05)
count0.05<-numeric()
for (i in 1:12){
count0.05[i]<-sum(condition0.05[,i]==1)}

threshold <- 0.1
condition0.1 <- ifelse(res< threshold, 1, 0)

condition0.1<-as.data.frame(condition0.1)
count0.1<-numeric()
for (i in 1:12){
count0.1[i]<-sum(condition0.1[,i]==1)}

```

```{r}
reduced<-survey_data[,-c(3,14)]
```

```{r}
saveRDS(res,"../../data/pvalues_cat.RData")
saveRDS(reduced,"../../data/survey_reduced.RData")

```
 
```{r}
res<-readRDS("../../data/pvalues_cat.RData")
```

## Two-way Anova

```{r}
survey_data<-readRDS("../../data/survey_reduced.RData")
res<-readRDS("../../data/pvalues_cat.RData")
```

###energy:age, abroad 
reject HO-> keep interaction
p-value:0.048
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$energy~ survey_data$age+ survey_data$estero+survey_data$age:survey_data$estero))[[1]][3,4]  
T0_stat

aov.H0 <- aov(median_data$energy~ survey_data$age+ survey_data$estero)
aov.H0

residuals.H0 <- aov.H0$residuals 
n = length(median_data$energy)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$age + survey_data$estero + survey_data$age:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
### liveness: sex,abroad
accept H0-> no interaction
p-value 0.427

```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$liveness~ survey_data$sesso+ survey_data$estero+survey_data$sesso:survey_data$estero))[[1]][3,4]  
T0_stat

aov.H0 <- aov(median_data$liveness~ survey_data$sesso+ survey_data$estero)
aov.H0

residuals.H0 <- aov.H0$residuals 
n = length(median_data$liveness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$sesso + survey_data$estero + survey_data$sesso:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
### acusticness: age,abroad,work (no interactions)

H1 all interaction, H0 no 3 interactions
accept H0
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero+survey_data$lavoro:survey_data$estero:survey_data$age))[[1]][3,4]  


aov.H0 <- aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$acousticness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero+survey_data$lavoro:survey_data$estero:survey_data$age))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
H1 as before H0 remove estero:lavoro
accept H0
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]  


aov.H0 <- aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$acousticness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
H1 as before H0 remove estero:age
accept H0


```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]  


aov.H0 <- aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$acousticness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
H1 as before H0 remove lavoro:age
accept H0

-> no interactions
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age))[[1]][3,4]  


aov.H0 <- aov(median_data$acousticness~ survey_data$lavoro+ survey_data$age+ survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$acousticness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$lavoro+ survey_data$age+ survey_data$estero+survey_data$lavoro:survey_data$age))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
### loudness: age, abroad, instrument (no interactions)

H1 all interaction, H0 no 3 interactions
accept H0

```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age+survey_data$age:survey_data$estero+survey_data$strumento:survey_data$estero:survey_data$age))[[1]][3,4]  


aov.H0 <- aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age+survey_data$age:survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$loudness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age+survey_data$age:survey_data$estero+survey_data$strumento:survey_data$estero:survey_data$age))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```

H0 remove age:estero
accept H0
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]  


aov.H0 <- aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$loudness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age+survey_data$age:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
H0 remove age:strumento
accept H0
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age))[[1]][3,4]  


aov.H0 <- aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$loudness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero+survey_data$strumento:survey_data$age))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```
H0 remove estero:strumento
accept H0
-> no interactions
```{r}
B=1000

T0_stat <- summary.aov(aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero))[[1]][3,4]  


aov.H0 <- aov(median_data$loudness~ survey_data$strumento+ survey_data$age+ survey_data$estero)


residuals.H0 <- aov.H0$residuals 
n = length(median_data$loudness)


T_stat <- numeric(B)
for(perm in 1:B){
  permutation <- sample(n)
  # permute the residuals
  residuals.H0 <- residuals.H0[permutation]
  perm.response.H0 <- aov.H0$fitted + residuals.H0
  # re-fit full model to calculate statistic
  T_stat[perm] <- summary.aov(aov(   perm.response.H0  ~ survey_data$strumento+ survey_data$age+ survey_data$estero+survey_data$strumento:survey_data$estero))[[1]][3,4]
}
sum(T_stat >= T0_stat)/B
```

## Results
popularity: sex
acousticness: age, abroad, work (no interaction)
danceability: books
energy: age, abroad (interaction)
instrumentalness: abroad
liveness : sex, abroad (no interaction)
loudness: age, abroad, instrument (no interaction)
speechiness: 
tempo: work
valence: genere
duration:
year:
```{r}
count0.05
colnames(res)
```
## Cluster by Kmode (da rivedere)

```{r}
library(klaR)
colSums(is.na(survey_data))
k_data<-survey_data[,-c(3,8,13,15)]
k_data<-as.data.frame(lapply(k_data, as.factor))
res_clust<-kmodes(k_data, 4, iter.max = 15, weighted = FALSE, fast = TRUE)
```

```{r}

cost <- numeric(length = 10)
silhouette_scores <- numeric(length = 10)

for (i in 2:10) {
  kmodes_model <- kmodes(k_data, i, iter.max = 15, weighted = FALSE, fast = TRUE)
  cost[i] <- kmodes_model$withindiff

}

plot(2:10, cost[2:10], type = "b", pch = 19, frame = FALSE, 
     xlab = "Number of Clusters", ylab = "Cost")
```
```{r}
library(ggplot2)

k_data$cluster <- as.factor(res_clust$cluster)
table(k_data$cluster)


ggplot(k_data, aes(x = sesso, y = libri, color = cluster)) +
  geom_point() +
  labs(title = "Cluster Plot")
```



```{r}

```

