---
title: 'Preprocess_numeric'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(848)
```

# Libraries
```{r}
library(dplyr)
```


##Upload useful function and load data
```{r}
source("normalize_numeric_global.R")
dataset_list = readRDS("../../data/data_list.RData")
```


##Remove dataframe in the list that are of too poor/rich of data
```{r}
#clean dataset
n_row <- numeric(length(dataset_list ))

for (i in seq_along(dataset_list )) {
  n_row[i] <- nrow(dataset_list [[i]])
}

hist(n_row,main = "before")
# Function to filter out data frames with wrong nrow and crop the one too long
filter_nrow <- function(df) {
  nrow(df) > 5
}


filtered_list <- Filter(filter_nrow, dataset_list)
filtered_list[[26]] <- filtered_list[[26]][1:101, ]
dataset_list<- filtered_list

n_row <- numeric(length(dataset_list ))
for (i in seq_along(dataset_list )) {
  n_row[i] <- nrow(dataset_list [[i]])
}
hist(n_row, main = "after")

```
## Preprocess numeric data
This chunk provides numeric data normalized in a global way
Note that the covariates *duration* and *years* are not normalized on purpose
```{r}

numeric_list <- list()
for (i in seq_along(dataset_list)) {
  data <- dataset_list[[i]]
  numeric_list[[i]] <- data[, c(5, 7:15, 18, 19)]
}
numeric_list <- normalize_numeric_global(numeric_list)

combined_numeric <- do.call(rbind, numeric_list)
combined_numeric <-round(combined_numeric,3)

names<-names(dataset_list)
temp <- rep(names, times = n_row)
combined_numeric$id<-temp

head(combined_numeric)
dim(combined_numeric)
```
Let's save in two different dataframes the mean and variance  for each variable in each playlist


```{r}
temp<-combined_numeric
temp <- temp %>%
  group_by(id) %>%
  summarize_all(mean)

mean_df<-temp
mean_df$id<-names(dataset_list)

temp<-combined_numeric
temp <- temp %>%
  group_by(id) %>%
  summarize_all(var)

variance_df<-temp
variance_df$id<-names(dataset_list)

```

## Save data
```{r}
saveRDS(combined_numeric,"../../data/data_numeric_cleaned2.RData")
saveRDS(mean_df,"../../data/data_mean.RData")
saveRDS(variance_df,"../../data/data_variance.RData")
```


```{r}
tt= readRDS("../../data/data_numeric_cleaned2.RData")
```


## Visualise numeric data
```{r}
#use this to have a boxplot of the variables you want to visualize
#change this line with the number of the numeric dataset you want to open
numeric<-numeric_list[[9]]

par(mfrow = c(2, 3))
numeric<-numeric_list[[45]]
col_names<-colnames(numeric)
boxplot(numeric[,1:2], col = "lightblue", main = "Boxplots", names = col_names[1:2], cex.axis = 0.5)
boxplot(numeric[,3:4], col = "lightblue", main = "Boxplots", names = col_names[3:4], cex.axis = 0.5)
boxplot(numeric[,5:6], col = "lightblue", main = "Boxplots", names = col_names[5:6], cex.axis = 0.5)
abline(h=c(0.5,0.8),col="red")
boxplot(numeric[,7:8], col = "lightblue", main = "Boxplots", names = col_names[7:8], cex.axis = 0.5)
boxplot(numeric[,9:10], col = "lightblue", main = "Boxplots", names = col_names[9:10], cex.axis = 0.5)
par(mfrow = c(1, 2))
boxplot(numeric[,11], col = "lightblue", main = "Duration", names = col_names[11], cex.axis = 0.5)
boxplot(numeric[,12], col = "lightblue", main = "Year", names = col_names[12], cex.axis = 0.5)

```


## Cluster by k_mean
Obv in order to apply k-mean we need scaled variables so we are gonna scale *duration* and *year* as well

Rescale data and esclude id from clusterization
```{r}
temp<-combined_numeric
  
min_max_normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}
  
temp$duration<-  min_max_normalize(temp[,11])
temp$year<-  min_max_normalize(temp[,12])

scaled_data<-temp
cluster_subset <- temp[, -which(names(temp) == "id")]
```

Try to inspect with elbow method the number of clusters to build
(non converge.. provo con 8)
```{r}
library(factoextra)
fviz_nbclust(cluster_subset, kmeans, method = "wss")
```

```{r}
k<-8
kmeans_result <- kmeans(scaled_data, centers = k)
clustered <- cbind(combined_numeric, cluster = kmeans_result$cluster)
aggregate(cluster_subset, by = list(cluster = clustered$cluster), FUN = mean)
```
Asses the quality of the clustering
By now I've used euclidean distance to compute distance between data, but could be useful
to take into account correlation between covariates (so maybe mahalanobis)


```{r}
library(cluster)
dist_matrix <- as.matrix(dist(cluster_subset, method ="euclidean" ))
silhouette_score <- silhouette(kmeans_result$cluster, dist_matrix)
summary(silhouette_score)
```
## PCA

So far no satisfactory result, maybe better to try Pca and then do clustering on latent variables

```{r}

library(FactoMineR)
```

```{r}

pca_result <- PCA(cluster_subset, graph = FALSE)
summary(pca_result)  

plot(pca_result, choix = "var") 

```
we need at least 8 dim to take into account 80% of the variability
(first five almost 65%)
1 dim-> +loudness, +energy,-acusticness
2 dim-> +duration, -year, -speechiness, -danceability
3 dim-> -pop,-danceability, +speechiness
4 dim-> -pop, +liveness
5 dim-> +tempo, -liveness

risultati abbastanza confusi e direi soprattutto non affidabili..


## Preprocessing factors


```{r}
factor_list <- list()
for (i in seq_along(dataset_list)) {
  data <- dataset_list[[i]]
factor_list[[i]] <- data[,c(2,3,4,6,16,17,20:ncol(data))]
}
```

###Cleaning genres

function to rename the single genre
```{r}
transform_genre <- function(old_g){
  worlds <- unlist(strsplit(old_g, " "))
  

  pop <- c("indie", "pop", "Indie", "Pop", "hyperpop", "mellow", "britpop", "folk-pop", "boy", "dreamo", "europop", "show", "romantic", "austropop", "bubblegum", "cartoni", "group", "electropop", "afropop", "beat", "austindie", "standards", "broadway", "musical", "tontipop","etherpop", "cover","nederpop","c86", "alley", "sophisti-pop")
  
  rock <- c("rock", "alternative", "rock-and-roll", "beatlesque", "madchester", "punk", "alt", "revival", "shoegaze", "grunge", "j-rock", "bubblegrunge","emo")
  
  electronic <- c("techno", "wave", "electropowerpop", "afrofuturism", "electro", "disco", "edm", "dembow", "tech", "psytrance","afrobeat", "touch", "tekk", "chillwave","vapor", "cubaton", "house", "electronic", "afrobeats", "indietronica", "downtempo", "brostep", "room", "fi", "lo-fi", "ambient", "ai", "afroswing", "acidcore", "soundtrack", "ambient", "experimental", "dance", "electronica", "folktronica", "eurodance", "aussietronica", "psych","basshall", "neo-psychedelic", "covertronica", "easy", "electra", "hi-nrg", "balearic","bass", "speedrun", "video", "dub", "chiptune", "moombahton", "lounge", "weirdcore", "dancehall", "vogue")
  
  hiphop <- c("rap", "trap", "hip", "drill", "urbano", "reggaeton", "phonk", "grime", "plugg", "neoperreo")
  
  country <- c("country", "tejano")
  
  jazz <- c("jazz", "blues", "bebop", "bossa", "americana", "melancholia", "post-bop")
  
  classical <- c("classical", "orchestra", "chamber", "baroque", "violin")
  
  folk <- c("folk", "cantautorato", "autore", "d'autore", "singer-songwriter", "neomelodici", "cantautora", "musica", "anime", "brasileiro", "tuareg", "sebene", "chicha", "bajki", "cumbia", "bachata", "cha-cha-cha", "cantautor", "mariachi", "bolero", "christian", "ccm", "canzone", "celtic", "chanson", "cappella", "canadian", "native", "mambo", "stomp", "mpb", "flamenco", "ska", "calypso")
  
  soul <- c("soul", "R&B", "funk", "r&b", "reggae", "groove", "funky", "charango", "motown", "souldies", "storm", "afro-funk")
  
  metal <- c("metal", "metalcore", "deathcore", "slayer", "djent")
  
  missing <- c("previa", "fluxwork", "metropopolis", "meme", "bossbeat", "comic", "concurso")
  
  #l'output della funzione è il nuvo genere
  if (is.na(old_g)){
    return ("missing")
  }
  if (any(!is.na(match(worlds, pop)))){
    return ("pop")}
  if (any(!is.na(match(worlds, rock)))){
    return ("rock")}
  if (any(!is.na(match(worlds, electronic)))){
    return ("electronic")}
  if (any(!is.na(match(worlds, hiphop)))){
    return ("hiphop")}
  if (any(!is.na(match(worlds, country)))){
    return ("country")}
  if (any(!is.na(match(worlds, jazz)))){
    return ("jazz")}
  if (any(!is.na(match(worlds, classical)))){
    return ("classical")}
  if (any(!is.na(match(worlds, folk)))){
    return ("folk")}
  if (any(!is.na(match(worlds, soul)))){
    return ("soul")}
  if (any(!is.na(match(worlds, metal)))){
    return ("metal")}
  if (any(!is.na(match(worlds, missing)))){
    return ("missing")
  }
  return (old_g)
}


```

function to update genres of the playlist
```{r}
transform_playlist <- function(genre) {
  #matching_indices <- c()
  for (i in 1:dim(genre)[1]) {
    new_g <- transform_genre(genre[i,])
   genre[i,] <- new_g
  }
  #print (genre[matching_indices,])
  return(unlist(genre))
}
```

Updating factor list
```{r}
for (i in 1:69){
  temp<-factor_list[[i]]
  old_g <- temp["genre_1"]
  factor_list[[i]] <- factor_list[[i]][, 1:8]
  factor_list[[i]]$genre <- transform_playlist(old_g)
  
}
```


```{r}
combined_factor <- do.call(rbind,factor_list)
names<-names(dataset_list)
temp <- rep(names, times = n_row)
combined_factor$id<-temp
id_playlists <- unique(combined_factor$id)
combined_factor<- as.data.frame(lapply(combined_factor, as.factor))
```

### Diversity coefficient
$$ D=1-N_a/N_p$$
The more D increase the more artists in the playlist

```{r}
survey_data<-readRDS("../../data/Surveycleaned.RData")
```

```{r}
compute_D <- function(df) {
  # Inizializza un vettore per immagazzinare i valori di D
  results_D <- numeric(69)

  # Itera su ogni riga del dataframe
  for (i in 1:69) {
    # Estrai l'id della playlist corrente
    
    # Filtra il dataframe per la playlist corrente
    playlist_current <- df[df$id == id_playlists[i], ]

    # Calcola il numero unico di artisti (Na)
    artists <- length(unique(playlist_current$artists))

    # Calcola il numero di canzoni nella playlist (Np)
    num_songs <- nrow(playlist_current)

    # Calcola il valore D e assegnalo alla posizione corrente nel vettore risultati_D
    results_D[i] <- artists /   num_songs
    
    
    survey_data[which(survey_data$id == id_playlists[i]), "D_coef"] <- results_D[i]


  }

  # Restituisci il dataframe con la colonna 'D' aggiunta
  return(survey_data )
}

```

```{r}
survey_data<- compute_D(combined_factor)
```

## Cluster by gneres, artists, key

idea alternativa costruire matrice simmetrica contenente numero di artisti 
uguali tra pe 6 playlist e applicare a quest'ultima una distanza che classifichi 
le persone in cluster 

```{r}
subset<-combined_factor[,c(2,5,9,10)]
```



```{r}
library(klaR)


# Aggregate song data to playlist level
subset <- aggregate(. ~ id, data = subset, function(x) toString(unique(x)))

# Apply kmodes clustering
result <- kmodes(subset[, c("artists", "key", "genre")], modes = 4, iter.max = 10)

# Display the cluster assignments
cluster_assignments <- result$cluster

# Visualize 
library(vcd)

clustered_data <- cbind(result$cluster, subset[, c("artists", "key", "genre")])
subset<- as.data.frame(lapply(subset, as.factor))
mosaic(clustered_data)
????
```
 
 


## Ideas
fit kernel density estimation in order to have a distribution for each on of the covariates
