---
title: 'Preprocess_numeric'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(848)
```

Libraries
```{r}
library(dplyr)
```


Upload useful function and load data
```{r}
source("normalize_numeric_global.R")
dataset_list = readRDS("data_final/data_list.RData")
```


Remove dataframe in the list that are of too poor/rich of data
```{r}
#clean dataset
n_row <- numeric(length(dataset_list ))

for (i in seq_along(dataset_list )) {
  n_row[i] <- nrow(dataset_list [[i]])
}

hist(n_row,main = "before")
# Function to filter out data frames with wrong nrow and crop the one too long
filter_nrow <- function(df) {
  nrow(df) > 5
}


filtered_list <- Filter(filter_nrow, dataset_list)
filtered_list[[26]] <- filtered_list[[26]][1:101, ]
dataset_list<- filtered_list

n_row <- numeric(length(dataset_list ))
for (i in seq_along(dataset_list )) {
  n_row[i] <- nrow(dataset_list [[i]])
}
hist(n_row, main = "after")

```

## Preprocessing numeric data

This chunk provides numeric data normalized in a global way
Note that the covariates *duration* and *years* are not normalized on purpose
```{r}

numeric_list <- list()
for (i in seq_along(dataset_list)) {
  data <- dataset_list[[i]]
  numeric_list[[i]] <- data[, c(5, 7:15, 18, 19)]
}
numeric_list <- normalize_numeric_global(numeric_list)

combined_numeric <- do.call(rbind, numeric_list)
combined_numeric <-round(combined_numeric,3)

names<-names(dataset_list)
temp <- rep(names, times = n_row)
combined_numeric$id<-temp

head(combined_numeric)
dim(combined_numeric)
```
Let's save in two different dataframes the mean and variance  for each variable in each playlist
to consider a first quantitative coarse analysis 


```{r}
temp<-combined_numeric
temp <- temp %>%
  group_by(id) %>%
  summarize_all(mean)

mean_df<-temp
mean_df$id<-names(dataset_list)

temp<-combined_numeric
temp <- temp %>%
  group_by(id) %>%
  summarize_all(var)

variance_df<-temp
variance_df$id<-names(dataset_list)

```

Save cleaned numeric data
```{r}
saveRDS(combined_numeric,"data_final/data_numeric_cleaned.RData")

```

## Visualize numeric data
```{r}
#use this to have a boxplot of the variables you want to visualize
#change this line with the number of the numeric dataset you want to open
numeric<-numeric_list[[9]]

par(mfrow = c(2, 3))
numeric<-numeric_list[[45]]
col_names<-colnames(numeric)
boxplot(numeric[,1:2], col = "lightblue", main = "Boxplots", names = col_names[1:2], cex.axis = 0.5)
boxplot(numeric[,3:4], col = "lightblue", main = "Boxplots", names = col_names[3:4], cex.axis = 0.5)
boxplot(numeric[,5:6], col = "lightblue", main = "Boxplots", names = col_names[5:6], cex.axis = 0.5)
abline(h=c(0.5,0.8),col="red")
boxplot(numeric[,7:8], col = "lightblue", main = "Boxplots", names = col_names[7:8], cex.axis = 0.5)
boxplot(numeric[,9:10], col = "lightblue", main = "Boxplots", names = col_names[9:10], cex.axis = 0.5)
par(mfrow = c(1, 2))
boxplot(numeric[,11], col = "lightblue", main = "Duration", names = col_names[11], cex.axis = 0.5)
boxplot(numeric[,12], col = "lightblue", main = "Year", names = col_names[12], cex.axis = 0.5)

```



## Preprocessing factors


```{r}
factor_list <- list()
for (i in seq_along(dataset_list)) {
  data <- dataset_list[[i]]
factor_list[[i]] <- data[,c(2,3,4,6,16,17,20:ncol(data))]
}
```

Cleaning genres

```{r}
#function to rename the single genre
transform_genre <- function(old_g){
  worlds <- unlist(strsplit(old_g, " "))
  

  pop <- c("indie", "pop", "Indie", "Pop", "hyperpop", "mellow", "britpop", "folk-pop", "boy", "dreamo", "europop", "show", "romantic", "austropop", "bubblegum", "cartoni", "group", "electropop", "afropop", "beat", "austindie", "standards", "broadway", "musical", "tontipop","etherpop", "cover","nederpop","c86", "alley", "sophisti-pop")
  
  rock <- c("rock", "alternative", "rock-and-roll", "beatlesque", "madchester", "punk", "alt", "revival", "shoegaze", "grunge", "j-rock", "bubblegrunge","emo")
  
  electronic <- c("techno", "wave", "electropowerpop", "afrofuturism", "electro", "disco", "edm", "dembow", "tech", "psytrance","afrobeat", "touch", "tekk", "chillwave","vapor", "cubaton", "house", "electronic", "afrobeats", "indietronica", "downtempo", "brostep", "room", "fi", "lo-fi", "ambient", "ai", "afroswing", "acidcore", "soundtrack", "ambient", "experimental", "dance", "electronica", "folktronica", "eurodance", "aussietronica", "psych","basshall", "neo-psychedelic", "covertronica", "easy", "electra", "hi-nrg", "balearic","bass", "speedrun", "video", "dub", "chiptune", "moombahton", "lounge", "weirdcore", "dancehall", "vogue")
  
  hiphop <- c("rap", "trap", "hip", "drill", "urbano", "reggaeton", "phonk", "grime", "plugg", "neoperreo")
  
  country <- c("country", "tejano")
  
  jazz <- c("jazz", "blues", "bebop", "bossa", "americana", "melancholia", "post-bop")
  
  classical <- c("classical", "orchestra", "chamber", "baroque", "violin")
  
  folk <- c("folk", "cantautorato", "autore", "d'autore", "singer-songwriter", "neomelodici", "cantautora", "musica", "anime", "brasileiro", "tuareg", "sebene", "chicha", "bajki", "cumbia", "bachata", "cha-cha-cha", "cantautor", "mariachi", "bolero", "christian", "ccm", "canzone", "celtic", "chanson", "cappella", "canadian", "native", "mambo", "stomp", "mpb", "flamenco", "ska", "calypso")
  
  soul <- c("soul", "R&B", "funk", "r&b", "reggae", "groove", "funky", "charango", "motown", "souldies", "storm", "afro-funk")
  
  metal <- c("metal", "metalcore", "deathcore", "slayer", "djent")
  
  missing <- c("previa", "fluxwork", "metropopolis", "meme", "bossbeat", "comic", "concurso")
  
  #l'output della funzione è il nuvo genere
  if (is.na(old_g)){
    return ("missing")
  }
  if (any(!is.na(match(worlds, pop)))){
    return ("pop")}
  if (any(!is.na(match(worlds, rock)))){
    return ("rock")}
  if (any(!is.na(match(worlds, electronic)))){
    return ("electronic")}
  if (any(!is.na(match(worlds, hiphop)))){
    return ("hiphop")}
  if (any(!is.na(match(worlds, country)))){
    return ("country")}
  if (any(!is.na(match(worlds, jazz)))){
    return ("jazz")}
  if (any(!is.na(match(worlds, classical)))){
    return ("classical")}
  if (any(!is.na(match(worlds, folk)))){
    return ("folk")}
  if (any(!is.na(match(worlds, soul)))){
    return ("soul")}
  if (any(!is.na(match(worlds, metal)))){
    return ("metal")}
  if (any(!is.na(match(worlds, missing)))){
    return ("missing")
  }
  return (old_g)
}

```

function to update genres of the playlist
```{r}
transform_playlist <- function(genre) {
  #matching_indices <- c()
  for (i in 1:dim(genre)[1]) {
    new_g <- transform_genre(genre[i,])
   genre[i,] <- new_g
  }
  #print (genre[matching_indices,])
  return(unlist(genre))
}
```

Updating factor list
```{r}
for (i in 1:69){
  temp<-factor_list[[i]]
  old_g <- temp["genre_1"]
  factor_list[[i]] <- factor_list[[i]][, 1:8]
  factor_list[[i]]$genre <- transform_playlist(old_g)
  
}
```


```{r}
combined_factor <- do.call(rbind,factor_list)
names<-names(dataset_list)
temp <- rep(names, times = n_row)
combined_factor$id<-temp
id_playlists <- unique(combined_factor$id)
combined_factor<- as.data.frame(lapply(combined_factor, as.factor))
saveRDS(combined_factor,"data_final/data_factor_cleaned.RData")
```

## Preprocessing Surveys

Load Data Surveys

```{r}
Survey_data = readRDS("../data/Questionario_eng.RData")
Quest_data = readRDS("../data/Questionario.RData")
```

Rename cols

```{r}
names_cols<-c("age", "sesso", "educazione", "campo.studi", "stato", "libri", "lavoro", "importanza.musica", "genere", "come.ascolti.musica","quando.ascolti.musica", "concerti", "strumento", "sport", "estero", "politica", "hobby", "regione", "abitanti.citta", "id" )
names(Quest_data)<-names_cols
names(Survey_data)<-names_cols
```

Merging dataframes

```{r}
Data<-rbind(Quest_data, Survey_data)
```

```{r}
dataset_list = readRDS("data_final/data_list.RData")
id_keep<-names(dataset_list)
```

we keep only the rows corresponding to people having a proper playlist

```{r}
filtered_data <- Data[Data$id %in% id_keep, ]
```

Adjusting factors ->Grammar corrections..

```{r}
temp<-filtered_data$importanza.musica
temp[7]="tanto"
filtered_data$importanza.musica<-temp
```

```{r}
temp<-filtered_data$strumento
temp[11]="piano"
temp[29]="chitarra"
filtered_data$strumento<-temp
```


```{r}
temp<-filtered_data$politica
temp[c(68)]="Si molto"
filtered_data$politica<-temp
```

```{r}
temp<-filtered_data$abitanti.citta
temp[c(69)]= "Tra 100.000 e 500.000 abitanti"
temp[c(64,65,66,67,68,70)]="Pi? di 500 000 abitanti" 
temp[1]="Tra 100.000 e 500.000 abitanti"
filtered_data$abitanti.citta<-temp
```

```{r}
temp<-filtered_data$estero
temp[c(1,64,65,66,67,68,69,70)]= "Europa occidentale"
filtered_data$estero<-temp
```

People not living in Italy or no longer living in Italy ->"/"

```{r}
temp<-filtered_data$regione
Lombardia<-c(5,9,13,15,17,19,25,27,29,33,35,41,43,45,53,55,59,61,63,4,6,8,12,14,18,20,22,36,40,42,44,46,48,50,52,54,56,58,60,62)
na<-c(11,23,34,47,64:70)
Lazio<-c(7,57,28,38)
Toscana<-c(1,21,37,16,30,31,32,49)
temp[Lombardia]<-"Lombardia"
temp[na]="/"
temp[Lazio]="Lazio"
temp[Toscana]="Toscana"
filtered_data$regione<-temp
```


Collecting people playing more then  one instrument
```{r}
index<-c(2,28,57,70)
filtered_data$strumento[index]="2+"

```

Converting to factors

```{r}
filtered_data$sesso<-as.factor(filtered_data$sesso)
filtered_data$educazione<-as.factor(filtered_data$educazione)
filtered_data$campo.studi<-as.factor(filtered_data$campo.studi)
filtered_data$libri<-as.factor(filtered_data$libri)
filtered_data$lavoro<-as.factor(filtered_data$lavoro)
filtered_data$importanza.musica<-as.factor(filtered_data$importanza.musica)
filtered_data$come.ascolti.musica<-as.factor(filtered_data$come.ascolti.musica)
filtered_data$politica<-as.factor(filtered_data$politica)
filtered_data$abitanti.citta<-as.factor(filtered_data$abitanti.citta)
filtered_data$estero<-as.factor(filtered_data$estero)
filtered_data$sport<-as.factor(filtered_data$sport)

```

 I had to adjust capslocks in order to have unique levels 
 
```{r}
col.stato<-filtered_data$stato
Italia<- c(1,2,3,4,5,6,8,9,10,12,13,14,15,16,17,18,19,20,21,22,24,25,26,27,28,29,30,31,32,33,35,36,37,38,39,40,41,42,43,44,45,46,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,67)
Svizzera<-c(7,23)
Germania<-c(34,70)
Olanda<-c(47)
Spagna<-c(11,68,69)
Canada<-c(64,65,66)
col.stato[Canada]="Canada"
col.stato[Italia]="Italia"
col.stato[Spagna]="Spagna"
col.stato[Svizzera]="Svizzera"

col.stato<-as.factor(col.stato)
levels(col.stato)
```
```{r}
filtered_data$stato<-col.stato
```

removing the guy with only 3 songs in the playlist
the one with id: "4YjSpxvniwzXvBB"

```{r}
filtered_data<-filtered_data[-which(filtered_data$id=="4YjSpxvniwzXvBB"),]
```

Process genres in the surveys

```{r}
transform_genre <- function(old_g){

  worlds <- unlist(strsplit(old_g, " "))
  

  pop <- c("Pop-rock","indie","pop","Indie","Pop","Pop/Indie","Pop-commerciale", "emergente")
  
  rock <- c("rock", "Pop/Rock","Rock", "Rock/pop")
  
  electronic <- c("EDM","elettronica")
  
  hiphop <- c("Rap","hop","urban", "rap/trap", "Raggaetton","Spanish","rap")
  
  country <- c()
  
  jazz <- c("Jazz","blues")
  
  classical <- c("Classica")
  
  folk <- c("Cantautori","italiano", "italiana")
  
  soul <- c( "r&b;")
  
  metal <- c("Metal")
  
  missing <- c("Non","non"," ")
  
  #l'output della funzione è il nuvo genere
  if (is.na(old_g)){
    return ("missing")
  }
  if (any(!is.na(match(worlds, rock)))){
    return ("rock")}
  if (any(!is.na(match(worlds, pop)))){
    return ("pop")}
  if (any(!is.na(match(worlds, electronic)))){
    return ("electronic")}
  if (any(!is.na(match(worlds, hiphop)))){
    return ("hiphop")}
  if (any(!is.na(match(worlds, country)))){
    return ("country")}
  if (any(!is.na(match(worlds, jazz)))){
    return ("jazz")}
  if (any(!is.na(match(worlds, classical)))){
    return ("classical")}
  if (any(!is.na(match(worlds, folk)))){
    return ("folk")}
  if (any(!is.na(match(worlds, soul)))){
    return ("soul")}
  if (any(!is.na(match(worlds, metal)))){
    return ("metal")}
  if (any(!is.na(match(worlds, missing)))){
    return ("missing")
  }
  return (old_g)
}

```

```{r}
genre<-filtered_data[,9]
for (i in 1:69){
 filtered_data[i,9]<-transform_genre(genre[i]) 
}
 filtered_data[1,9]="missing"

filtered_data$genere<-as.factor( filtered_data$genere)
```


Categorize *strumento*
```{r}
instrument=filtered_data[,13]
test<-instrument!="No"
instrument_new<-ifelse(test,"Si","No")
filtered_data[,13]<-instrument_new
filtered_data$strumento<-as.factor(filtered_data$strumento)
```

Categorize *regioni*

```{r}
filtered_data$regione[which(filtered_data$regione %in% c("Lombardia", "Veneto", "Emilia Romagna "))] <- "nord"
filtered_data$regione[which(filtered_data$regione %in% c("Toscana","Abruzzo"))] <- "centro"
filtered_data$regione[which(filtered_data$regione %in% c("Puglia", "Lazio"))] <- "sud"
filtered_data$regione[which(filtered_data$regione %in% c("/"))] <- "missing"
filtered_data$regione<-as.factor(filtered_data$regione)
```


## Visualize survey data


```{r}
reduced<-filtered_data[,-c(11,14,17)]
```

```{r}
summary(reduced)
```

Save processed data so far

```{r}
factor_columns<-c(2,3,4,5,6,7,8,9,10,12,13,14,15,16)
cols<-names(reduced[,factor_columns])
reduced_factors<-reduced[,factor_columns]
```


```{r}
library(ggplot2)
names<-colnames(reduced_factors)
do_barplot<-function(i){
ggplot(as.data.frame(reduced_factors)) + 
  geom_bar(mapping = aes(x =reduced_factors[[i]], fill = reduced_factors[[i]]))+
    ggtitle(names[i])}


```


```{r}
do_barplot(1)
do_barplot(2)
do_barplot(3)
do_barplot(4)
do_barplot(5)
do_barplot(6)
do_barplot(7)
do_barplot(8)
do_barplot(9)
do_barplot(10)
do_barplot(11)
do_barplot(12)
do_barplot(13)
```

Missing data analysis
```{r}
reduced[reduced == "/"] <- "NA"
reduced[reduced == "missing"] <- "NA"
na_counts <- colSums(is.na(reduced)) 
#11 NA in region given by people who live abroad, 4 NA in field of studies
```

Saving Survey data cleaned
```{r}
saveRDS(reduced,"data_final/Surveycleaned.RData")
```


## Diversity coefficient

This was used to assess the percentage of variance in the playlist of each individual

$$ D=1-N_a/N_p$$
The more D increase the more artists in the playlist

```{r}
survey_data<-readRDS("data_final/Surveycleaned.RData")
```

```{r}
compute_D <- function(df) {
  # Inizializza un vettore per immagazzinare i valori di D
  results_D <- numeric(69)

  # Itera su ogni riga del dataframe
  for (i in 1:69) {
    # Estrai l'id della playlist corrente
    
    # Filtra il dataframe per la playlist corrente
    playlist_current <- df[df$id == id_playlists[i], ]

    # Calcola il numero unico di artisti (Na)
    artists <- length(unique(playlist_current$artists))

    # Calcola il numero di canzoni nella playlist (Np)
    num_songs <- nrow(playlist_current)

    # Calcola il valore D e assegnalo alla posizione corrente nel vettore risultati_D
    results_D[i] <- artists /   num_songs
    
    
    survey_data[which(survey_data$id == id_playlists[i]), "D_coef"] <- results_D[i]


  }

  # Restituisci il dataframe con la colonna 'D' aggiunta
  return(survey_data )
}

```

```{r}
survey_data<- compute_D(combined_factor)
```



