---
title: 'Permutation'
author: "Alessandra Pescina"
date: "2023-11-22"
output: html_document
---

```{r}
library(dplyr)
```


## Loading numeric and survey data
```{r}
survey_data<-readRDS("../../data/Surveycleaned.RData")
numeric_data<-readRDS("../../data/data_numeric_cleaned2.RData")
```


```{r}
#Pertutaion test function
perm_t_test=function(x,y,iter=1e3){
  
  T0=abs(mean(x)-mean(y))  # define the test statistic
  T_stat=numeric(iter) # a vector to store the values of each iteration
  x_pooled=c(x,y) # pooled sample
  n=length(x_pooled)
  n1=length(x)
  
  for(perm in 1:iter){ # loop for conditional MC
    # permutation:
    permutation <- sample(1:n)
    x_perm <- x_pooled[permutation]
    x1_perm <- x_perm[1:n1]
    x2_perm <- x_perm[(n1+1):n]
    # test statistic:
    T_stat[perm] <- abs(mean(x1_perm) - mean(x2_perm))
    
  }
  
  # p-value
  p_val <- sum(T_stat>=T0)/iter
  return(p_val)
}
```

```{r}
#Permutation test on all the 12 covariates with extraction
set.seed(53)

my_perm <- function(cat1, cat2) {
  cols <- colnames(numeric_data)
  res <- vector("numeric", length = 12)

  for (j in 1:12) {
    p_value <- numeric(100)

    for (i in 1:100) {
      # Extract random indices based on geometric distribution
      indices1 <- sample(1:length(cat1), 1, prob = dgeom(1:length(cat1), prob = 0.1), replace = TRUE)
      indices2 <- sample(1:length(cat2), 1, prob = dgeom(1:length(cat2), prob = 0.1), replace = TRUE)

      cov1 <- numeric_data %>%
        filter(id == cat1[indices1]) %>%
        pull(cols[j])

      cov2 <- numeric_data %>%
        filter(id == cat2[indices2]) %>%
        pull(cols[j])

      p_value[i] <- perm_t_test(cov1, cov2)
    }

    res[j] <- mean(p_value)
  }

  return(res)
}

```





```{r}
#Non parametric one way anova function
one_way_anova <- function(x, cat, iter=1e-3){
  T_stat <- numeric(iter) 
  n <- dim(x)
  fit <- aov(weight ~ feed)
  T0 <- summary(fit)[[1]][1,4]
  for(perm in 1:iter){
    # Permutation:
    permutation <- sample(1:n)
    x_perm <- x[permutation]
    fit_perm <- aov(x_perm ~ cat)
  
    # Test statistic:
    T_stat[perm] <- summary(fit_perm)[[1]][1,4]
  }
  p_val <- sum(T_stat>=T0)/iter
  return (p_val)
} 

```

```{r}
#One way anova on all 12 covariates with extraction
set.seed(53)
my_one_way <- function(cat){
  res <- vector("numeric", length = 12)
  for (j in 1:12) {
    p_value <- numeric(100)

    for (i in 1:100) {
      # Extract random indices based on geometric distribution
      indices<- sample(1:nrows(numeric_data), 1, prob = dgeom(1:nrows(numeric_data), prob = 0.1), replace = TRUE)

      cov <- numeric_data %>%
        filter(id == cat[indices]) %>%
        pull(cols[j])
      
      p_value[i] <- one_way_anova(cov,cat)
    }

    res[j] <- mean(p_value)
  }
}

```


## Permutation Test each num_cov by sex

```{r}
cat1<-survey_data$id[survey_data$sesso=="Maschio"]
cat2<-survey_data$id[survey_data$sesso=="Femmina"]

```

```{r}
res_sex<-my_perm(cat1,cat2)
res_sex
```

## Permutation Test each num_cov by field of study
```{r}
test<-survey_data$campo.studi!="STEM (Science, Technology, Engineering, Mathematics)"         
survey_data$campo.studi<-ifelse(test,"Others","STEM (Science, Technology, Engineering, Mathematics)")
temp<-survey_data$id[!is.na(survey_data$campo.studi)]
selected_campostudi <- survey_data$campo.studi[!is.na(survey_data$campo.studi)]
cat1<-temp[selected_campostudi =="STEM (Science, Technology, Engineering, Mathematics)"]
cat2<-temp[selected_campostudi =="Others"]
```

```{r}
res_campo.studi<-my_perm(cat1,cat2) #pvalue year 0.059
```

## Permutation Test each num_cov by instrument

```{r}
cat1<-survey_data$id[survey_data$strumento=="Si"]
cat2<-survey_data$id[survey_data$strumento=="No"]

```

```{r}
res_instrument<-my_perm(cat1,cat2) #pvalue year 0.029
```

## Permutation Test each num_cov by country
```{r}
test<-survey_data$stato!="Italia"         
survey_data$stato<-ifelse(test,"Others","Italia")
temp<-survey_data$id[!is.na(survey_data$stato)]
selected_stato <- survey_data$stato[!is.na(survey_data$stato)]
cat1<-temp[selected_stato =="Italia"]
cat2<-temp[selected_stato =="Others"]
```

```{r}
res_country<-my_perm(cat1,cat2)
res_country #pvalue popolarità 0.087, danceability 0.066, energy 0.054, year 0.096 
#pvalue così buoni forse causati da campione piccolo di others
```

## Permutation Test each num_cov by number of books

```{r}
test<-survey_data$libri!="0"         
survey_data$libri<-ifelse(test,"1+","0")
temp<-survey_data$id[!is.na(survey_data$libri)]
selected_libri <- survey_data$libri[!is.na(survey_data$libri)]
cat1<-temp[selected_libri =="0"]
cat2<-temp[selected_libri =="1+"]
```

```{r}
res_books<-my_perm(cat1,cat2)
res_books #tutti i pvalue alti, ha senso non ci siano differenze
```
## Permutation Test each num_cov by abroad

```{r}
test<-survey_data$estero!="No"         
survey_data$estero<-ifelse(test,"Si","No")
temp<-survey_data$id[!is.na(survey_data$estero)]
selected_estero <- survey_data$estero[!is.na(survey_data$estero)]
cat1<-temp[selected_estero =="No"]
cat2<-temp[selected_estero =="Si"]
```

```{r}
res_abroad<-my_perm(cat1,cat2)
res_abroad #pvalue 0.094 energy, 0.098 year
```

##exploraton other categories

```{r}
# Subset the data based on the selected indices
selected_indices <- c(1,7:10,15,16)
selected_data <- survey_data[, selected_indices]

# Create bar plots for each selected variable

for (i in seq_along(selected_indices)) {
  x11()
  barplot(table(selected_data[, i]), col = "lightblue",
          main = colnames(selected_data)[i], xlab = "", ylab = "Frequency")
}

#conclusioni: -età under over (o 22.5 o 23.5), -lavoro anova (e poi si può fare pure si o no), -importanza musica boh, -genere anova (magari escludendo generi con bassa numerosità), -coem ascoli musica boh (non mi convince molto come categoria su cui lavortare), - regione anova. Ho escluso a priori concerti e politica, possiamo pensare se metetrli o no
```


## Permutation Test each num_cov by age

```{r}
# Count values below 22.5 in the 'age' column
values_below_22.5 <- sum(survey_data$età < 22.5, na.rm = TRUE)
values_below_22.5

# Count missing data in the 'age' column
missing_data_age <- sum(is.na(survey_data$età))
missing_data_age

```
```{r}
test<-survey_data$età < 22.5         
survey_data$età<-ifelse(test,"Under22.5","Over22.5")
temp<-survey_data$id[!is.na(survey_data$età)]
selected_età <- survey_data$età[!is.na(survey_data$età)]
cat1<-temp[selected_età =="Under22.5"]
cat2<-temp[selected_età =="Over22.5"]
```
```{r}
res_età<-my_perm(cat1,cat2)
res_età #pvalue tutti alti
```
## One way ANOVA each num_cov by job
```{r}
cat <- survey_data[7]
```

```{r}
res_lavoro <- my_one_way(cat)
```
















